The title

### 2016-10-20 analysis/paper/paper.Rmd
further organisation
Update: landform and west side of the river

@@

The landscape in the Lower Irrawaddy region is characterized by river terraces that are heavily incised. The uppermost terrace T1 is only sparsely preserved with one relict hill where the Chinthaungma monastery sits 70 m above the river level. Thick red gravel layers with a reddish-brown silty sand matrix overly the bedrock.

Terrace 2 (T2) can be distinguished by the scarcity of vegetation compared to the lower terrace 3 (T3). Probably due to the very thin or absent soil layer on top pf the bedrock, only grass, shrubs and some scattered trees grow on T2. The terrain is severely incised and has a lot of gently rolling gullies and valleys.

On T3, the vegetation is more prominent and there are fewer incisions. The red gravel layer is not as dominant as in T1, whereas the soil layer seems to be more pronounced. There are some filled fields and a golf course that was created in 1947 for the local oil workers. Because of its lower location, the gravels may be colluvial redposits from T1, although it could be an alluvial terrace.

According to Movius, two more terraces can be spotted from the river. After an intensive inspection, terrace 4 (T4) may be a cliff close to the river (base at 46 m) with a slight elevation  compared to the river (41 m). In contrast to the other terraces, the red gravel layer is absent on T4. However, the bedrock is overlain by coarse gravels in a reddish brown sandy silt matrix (5 cm) that is followed by a reddish brown fine grained sandy silt with occasional small gravel clasts, as well as small carbonate modules.

- descriptions of existing cuttings that we visited
- GPS data from transect
- surface finds of artefacts by KK

>>>>

The landscape in the Lower Irrawaddy region is characterized by a series of landforms on different levels on the eastern side of the river. There are sand cliffs that are heavily incised. On the west bank of the river, an old maeander of the Irrawaddy, but no terrace-like forms can be seen apart from the remnants of a plateau or peneplaned surface further inland. Another landscape feature is the geological fault zone east of Chauk, marking the base of the Shan scarp.

The uppermost landform (L1) is only sparsely preserved with one relict hill where the Chinthaungma monastery sits 70 m above the river level. Thick red gravel layers with a reddish-brown silty sand matrix overly the bedrock.

Landform 2 (L2) can be distinguished by the scarcity of vegetation compared to the lower landform 3 (L3). Probably due to the very thin or absent soil layer on top pf the bedrock, only grass, shrubs and some scattered trees grow on L2. The terrain is severely incised and has a lot of gently rolling gullies and valleys.

On L3, the vegetation is more prominent and there are fewer incisions. The red gravel layer is not as dominant as on L1, whereas the soil layer seems to be more pronounced. There are some filled fields and a golf course that was created in 1947 for the local oil workers. Because of its lower location, the gravels may be colluvial redposits from L1, although it could be an alluvial terrace.

According to Movius, two more levels can be spotted from the river. After an intensive inspection, the fourth landform (L4) may be a cliff close to the river (base at 46 m) with a slight elevation compared to the river (41 m). In contrast to the other levels, the red gravel layer is absent on L4. However, the bedrock is overlain by coarse gravels in a reddish brown sandy silt matrix (5 cm) that is followed by reddish brown fine grained sandy silt with occasional small gravel clasts, as well as small carbonate modules.

However, these landforms cannot be described as terraces for certain. There are indications that it might be terraces as elucidated by Movius, e.g. the gravels found on L1 and L3. But explicit terraces could not be identified in the field, especially due to the absence of terraces on the west side of the Irrawaddy River. More intensive cultivation and a very disturbed landscape could be reasons for that.

@@

## Surface finds of stone artefacts
